\cvsection{Experience}

\begin{cventries}
  \cventry
    {Head of Development} % Job title
    {\href{https://www.rieter.com}{Rieter AG}} % Organization
    {Rieter AG is a leading supplier of systems for short-staple fiber spinning, providing solutions and services across the entire textile value chain. The company specializes in machinery and technology for spinning, and downstream processes to enhance efficiency and quality in textile production.} %Organization Description
    {Winterthur, CH} % Location
    {2024} % Date(s)
    {
        \begin{cvitems}
            \item {\textbf{Strategic Leadership}: Directed a cross-regional development team of ~40 engineers (Czech Republic, Switzerland, India), implementing innovative production software solutions and scaling systems to support Rieter’s position as a leader in the textile manufacturing sector.}
            \item {\textbf{Digital Transformation Pioneer}: Spearheaded the organization’s digitalization journey, introducing cutting-edge technologies to optimize machine functionalities, automate maintenance processes, and enhance operational efficiency.}
            \item {\textbf{Executive Collaboration}: Partnered closely with C-level executives and Business Unit (BU) directors to align technological initiatives with corporate strategy, ensuring projects met both operational and strategic objectives.}
            \item {\textbf{Stakeholder Engagement}: Acted as the primary liaison between the development department and senior leadership, effectively communicating technical advancements, project roadmaps, and business impacts.}
            \item {\textbf{Budget \& Resource Optimization}: Manage 5M CHF budget for the whole department, including monthly and yearly forecasts and allocation.}
        \end{cvitems}
    }
  \cventry
  {Chief Technology Officer} % Job title
  {\href{https://www.aiones.ai}{Aiones}} % Organization
  {Aiones revolutionizes how companies approach process discovery and design, making it as straightforward as a conversation} %Organization Description
  {Vienna, AT} % Location
  {2024} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {\textbf{Technological Vision \& Leadership}: Co-founded Aiones and established the technological vision, integrating cutting-edge technologies such as Azure BOT APIs and OpenAI APIs to create innovative solutions for process discovery and design.}
      \item {\textbf{Process Professionalization}: Streamlined the development lifecycle by implementing Agile methodologies and introducing CI/CD pipelines through Azure DevOps, fostering a culture of efficiency and continuous delivery.}
      \item {\textbf{Infrastructure Scalability}: Architected a robust, scalable technology infrastructure on Azure to support extensive user testing and prepare for seamless product launches}
      \item {\textbf{Innovation Recognition}: Represented Aiones as a participant in the BoldBrain challenge, positioning the startup as a forward-thinking leader in process innovation.}
    \end{cvitems}
  }
%  \cventry
%    {Co-Founder} % Job title
%    {\href{https://www.idmodular.com}{ID Modular}} % Organization
%    {ID Modular is a startup aiming to create a new low-code/no-code platform in the digital identity world. Our goal is to make the Know Your Business / Customer (KYC / KYB) process creation extremely easy and affordable for other startups which need it. Even changing it later on would be as complex as a few clicks.} %Organization Description
%    {Lugano, CH} % Location
%    {2023} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Formulating and controlling the Business Plan execution}
%        \item {Leading the Fundraising activities}
%        \item {Providing technical guidance for the software development}
%      \end{cvitems}
%    }
  \cventry
    {Head Of Technology} % Job title
    {\href{https://www.bexio.com}{bexio AG}} % Organization
    {bexio is a Swiss market leader for cloud-based business software for small companies. Bexio software is now used by over 80'000 companies.} %Organization Description
    {Rapperswil, CH} % Location
    {2022 - 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Team Leadership}: Directed and mentored a diverse, high-performing global team, including 10+ near-shoring professionals across three countries, fostering collaboration, innovation, and accountability.}
        \item {\textbf{Infrastructure Modernization}: Transitioned the Site Reliability Engineering (SRE) team to a GitOps model, streamlining operations and enhancing the reliability of infrastructure supporting 80K+ customers.}
        \item {\textbf{Quality Culture Advocate}: Championed the introduction of Shift-Left testing principles, empowering the Quality Assurance team and coaching 5+ development teams to adopt a proactive quality-first mindset.}
        \item {\textbf{Architecting for Growth}: Built and led the Architecture Team from scratch, establishing a clear vision for long-term platform sustainability and creating a foundation for scalable growth.}
        \item {\textbf{Optimization}: Collaboratively modernized and optimized the platform stack, reducing recurring operational costs by 10\% while maintaining high performance and reliability}
      \end{cvitems}
    }

	\cventry
	{Head Of Development} % Job title
	{\href{https://www.e-globe-solutions.com}{e-globe solutions AG}} % Organization
  {e-globe solutions is a software company based in Bern, delivering custom IT solutions and integrations for the Fiber Optics market. Recently, it entered the SaaS world with "\href{https://www.godoo.ch}{godoo}", an orchestration tool for business workflows.} %Organization Description
	{Lugano, CH} % Location
	{2017 - 2022} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {\textbf{Comprehensive Leadership}: Directed a 12-member development team comprising specialists from junior to senior levels, fostering growth, innovation, and technical excellence.}
			\item {\textbf{Comprehensive Leadership}: Directed a 12-member development team comprising specialists from junior to senior levels, fostering growth, innovation, and technical excellence.}
			\item {\textbf{Product Ownership}: Served as Scrum Product Owner for the company’s flagship product, generating 60\%* of total revenue and driving its functional and architectural roadmap}
			\item {\textbf{Stakeholder Management \& Fundraising}: Successfully managed relationships with internal and external stakeholders to secure 5 MCHF in funding, supporting strategic initiatives.}
			\item {\textbf{Team Development \& Performance Management}: Instituted a structured feedback process, conducting regular performance evaluations and salary reviews to enhance employee satisfaction and productivity.}
			\item {\textbf{Cloud Transformation}: Migrated on-site services to AWS Cloud, achieving a 20\% reduction in development costs by December 2021 while enhancing scalability and reliability.}
			\item {\textbf{Efficiency Improvement}: Designed and implemented automation tools, boosting team productivity by 15\% over two years and streamlining operational workflows.}
		\end{cvitems}
	}

  \cventry
    {Solution Architect} % Job title
    {} % Organization
    {} %Organization Description
    {} % Location
    {2015 - 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Platform Development}: Designed a business workflow orchestration platform from the ground up, leveraging a React / .NET Core / Java / MySQL stack, ensuring robust functionality and scalability.}
        \item {\textbf{Infrastructure Innovation}: Implemented a Docker-based microservice infrastructure, reducing system downtime by 50\% in the first year and enhancing overall operational reliability.}
      \end{cvitems}
    }

  \cventry
    {Software Developer} % Job title
    {} % Organization
    {} %Organization Description
    {} % Location
    {2014 - 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Integration Development}: Developed real-time platform integrations and RESTful APIs using C\#/.NET Framework, adhering to RAML and Swagger standards for seamless system interoperability}
      \end{cvitems}
    }

\end{cventries}
